---
title: "Retrieving Substance Information"
author: "Matthew O'Meara"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Retrieving Substance Information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette describes several use cases for retrieving substance information from zinc15.docking.org using the `Zr` R package.

To follow along, make sure Zr package is installed

```{r, eval=F}
install.packages("devtools")
devtools::install_github("momeara/Zr")
```

And familiarize yourself with with http://zinc15.docking.org

## Searching for Substance info

Tanaka et al., (2015, 10.1371/journal.pone.0135657) observe uremic
solutes that accumulate when the kidneys fail. In Supplementary table
2, they list the 120 uremic compounds they observe. Here are the ones with HMDB Ids:

```{r, fig.show='hold'}
uremic_solutes <- c("HMDB00001", "HMDB00017", "HMDB00020", 
"HMDB00056", "HMDB00089", "HMDB00098", "HMDB00107", "HMDB00123", 
"HMDB00134", "HMDB00174", "HMDB00197", "HMDB00209", "HMDB00210", 
"HMDB00211", "HMDB00226", "HMDB00230", "HMDB00232", "HMDB00244", 
"HMDB00258", "HMDB00291", "HMDB00294", "HMDB00439", "HMDB00462", 
"HMDB00479", "HMDB00484", "HMDB00512", "HMDB00539", "HMDB00552", 
"HMDB00562", "HMDB00613", "HMDB00625", "HMDB00640", "HMDB00646", 
"HMDB00671", "HMDB00678", "HMDB00679", "HMDB00682", "HMDB00714", 
"HMDB00715", "HMDB00730", "HMDB00736", "HMDB00765", "HMDB00766", 
"HMDB00767", "HMDB00821", "HMDB00840", "HMDB00904", "HMDB00939", 
"HMDB00943", "HMDB00956", "HMDB00959", "HMDB01015", "HMDB01123", 
"HMDB01173", "HMDB01851", "HMDB01931", "HMDB02123", "HMDB02271", 
"HMDB02759", "HMDB02820", "HMDB02931", "HMDB02994", "HMDB03099", 
"HMDB03464", "HMDB03466", "HMDB03681", "HMDB03911", "HMDB04136", 
"HMDB04193", "HMDB04812", "HMDB04824", "HMDB04827", "HMDB06088", 
"HMDB06116", "HMDB06344", "HMDB06584", "HMDB06695", "HMDB11103", 
"HMDB11107", "HMDB11170", "HMDB11621", "HMDB11635", "HMDB11719", 
"HMDB11745", "HMDB11757", "HMDB12881", "HMDB13130", "HMDB13240", 
"HMDB13678", "HMDB13713", "HMDB29723", "HMDB29738", "HMDB32055", 
"HMDB34220", "HMDB41623", "HMDB59724", "HMDB60015", "HMDB60256", 
"HMDB61116")
```

To retrieve information about these compounds we can use `Zr` package

```{r, fig.show='hold'}
library(Zr)
library(dplyr)
s_info <- search_for_substances(uremic_solutes, verbose=T)
s_info %>% str
```
