---
title: "Retrieving Substance Information"
author: "Matthew O'Meara"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Retrieving Substance Information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette describes several use cases for retrieving substance information from zinc15.docking.org using the `Zr` R package.

To follow along, make sure Zr package is installed

```{r, eval=F}
install.packages("devtools")
devtools::install_github("momeara/Zr")
```

And familiarize yourself with with http://zinc15.docking.org

## Searching for Substance info

Tanaka et al., (2015, 10.1371/journal.pone.0135657) observe uremic
solutes that accumulate when the kidneys fail. In Supplementary table
2, they list the 120 uremic compounds they observe. Here are the ones with HMDB Ids:

```{r, fig.show='hold'}
uremic_solutes <- c("HMDB00001", "HMDB00017", "HMDB00020")
```

To retrieve information about these compounds we can use `Zr` package

```{r, fig.show='hold'}
library(Zr)
library(dplyr)
s_info <- search_for_substances(uremic_solutes, verbose=T)
s_info %>% str
```
